# 2. Creating Your First R Script

In this section, you will create your first R script.

## What is an R Script?

An **R script** is a file where you write R code.

R script files end with:

```text
.R
```

For example:

```text
first_script.R
```

An R script is useful because it saves your code. You can run the same code again later without retyping everything.

::: {.callout-tip}
## Tip

Use an R script when you want to save your work.

Use the Console when you want to quickly test one command.
:::

## Creating a New R Script

In RStudio:

1. Click **File**.
2. Click **New File**.
3. Click **R Script**.

<div class="screenshot-placeholder">

[Insert Screenshot: Creating a New R Script]

Show File > New File > R Script.

</div>

A blank script should open in the Source Pane.

## Basic Arithmetic

Before we work with data, let’s try R as a calculator.

Type the following into your script:

```{r}
2 + 3
10 - 4
5 * 6
20 / 4
```

These symbols mean:

| Symbol | Meaning |
|---|---|
| `+` | Add |
| `-` | Subtract |
| `*` | Multiply |
| `/` | Divide |

::: {.callout-note}
## Try It Yourself

Change the numbers and run the code again.

For example, try:

```r
100 / 5
12 * 3
```
:::

## Creating Variables

A **variable** is a name that stores a value.

For example:

```{r}
age <- 18
age
```

The symbol `<-` means “store this value.”

So this line:

```r
age <- 18
```

means:

> Store the number 18 in a variable called `age`.

## Why Use Variables?

Variables help us reuse information.

For example, instead of typing the same number many times, we can give it a name.

```{r}
quiz_score <- 92
homework_score <- 88

quiz_score
homework_score
```

Now we can use those variables in a calculation:

```{r}
final_score <- (quiz_score + homework_score) / 2
final_score
```

This code calculates the average of the quiz score and homework score.

## Printing Output

Sometimes you want to clearly print something.

You can use `print()`:

```{r}
print(final_score)
```

For simple work, typing the object name also shows the value:

```{r}
final_score
```

Both are okay.

::: {.callout-tip}
## Tip

In R, object names should not contain spaces.

Use this:

```r
quiz_score <- 92
```

Not this:

```r
quiz score <- 92
```
:::

## Adding Comments

A **comment** is a note to yourself or your reader.

In R, comments start with `#`.

R ignores comments when running code.

```{r}
# This stores my quiz score
quiz_score <- 92

# This prints the quiz score
quiz_score
```

Comments are useful because they help explain what your code is doing.

## Saving Your Script

To save your script:

1. Click **File**.
2. Click **Save**.
3. Name your file:

```text
first_script.R
```

4. Save it in your project folder.

<div class="screenshot-placeholder">

[Insert Screenshot: Saving an R Script]

Show the Save button and file name `first_script.R`.

</div>

::: {.callout-warning}
## Common Mistake

Do not save your script with a name like:

```text
Untitled1.R
```

Use a clear name, such as:

```text
first_script.R
```
:::

## Practice Exercise

::: {.callout-note}
## Practice

Create a new R script and write code that:

1. Stores your favorite number in a variable.
2. Stores your age in another variable.
3. Adds the two numbers together.
4. Prints the result.

Example:

```r
favorite_number <- 7
age <- 18
result <- favorite_number + age
print(result)
```
:::

## Check Your Understanding

Answer these questions in your own words:

1. What is an R script?
2. Why is it useful to save code in a script?
3. What does `<-` do?
4. What is the difference between these two lines?

```r
score <- 90
print(score)
```

## Summary

In this section, you learned how to:

- Create a new R script.
- Use R for basic arithmetic.
- Store values in variables.
- Print results.
- Add comments.
- Save your script.

You have now written your first R code!