# 7. Importing Data into R

Now that the CSV file is saved in your project folder, we can import it into R.

To **import data** means to bring data from a file into R so we can work with it.

## Importing a CSV File

Use this command:

```{r}
data <- read.csv("mydata.csv")
```

Let’s break it down.

| Part | Meaning |
|---|---|
| `data` | The name we are giving the dataset in R |
| `<-` | Stores something in an object |
| `read.csv()` | A function that reads CSV files |
| `"mydata.csv"` | The file name |

So this line means:

> Read the file called `mydata.csv` and store it in an object called `data`.

::: {.callout-tip}
## Tip

The file name must be inside quotation marks.
:::

## Looking at the First Few Rows

Use `head()` to see the first few rows:

```{r}
head(data)
```

This helps you quickly check that the data imported correctly.

## Understanding the Structure

Use `str()` to see the structure of the dataset:

```{r}
str(data)
```

This tells you:

- How many rows there are.
- How many columns there are.
- The names of the columns.
- The type of information in each column.

For example:

- Numbers may be shown as `int` or `num`.
- Words or categories may be shown as `chr`.

## Summarizing the Dataset

Use `summary()` to get a quick summary:

```{r}
summary(data)
```

For number columns, R may show:

- Minimum
- Median
- Mean
- Maximum

For text columns, R may show basic information about the values.

## Viewing Column Names

You can see the column names with:

```{r}
names(data)
```

## Plain-Language Explanation

If you run:

```r
head(data)
```

you are asking:

> Show me the first few students in the dataset.

If you run:

```r
str(data)
```

you are asking:

> What kind of information is stored in each column?

If you run:

```r
summary(data)
```

you are asking:

> Give me a quick overview of the dataset.

## Practice: Import and Inspect

::: {.callout-note}
## Practice

Import the dataset and answer these questions:

1. How many columns are in the dataset?
2. What are the column names?
3. What is one number column?
4. What is one category or text column?

Use these commands:

```r
data <- read.csv("mydata.csv")
head(data)
str(data)
summary(data)
names(data)
```
:::

## Common Mistake

::: {.callout-warning}
## Warning

This will not work if the file is not in your working directory:

```r
data <- read.csv("mydata.csv")
```

If you get a file not found error, go back to Section 5 and check your working directory.
:::

## Check Your Understanding

Answer these questions:

1. What does it mean to import data?
2. What does `read.csv()` do?
3. Why does `"mydata.csv"` need quotation marks?
4. What does `head(data)` show?
5. What does `summary(data)` show?

## Summary

In this section, you learned how to:

- Import a CSV file into R.
- Store the dataset in an object called `data`.
- View the first few rows.
- Check the structure of the dataset.
- Summarize the dataset.
- View column names.