# 8. Getting Results

Now that your data is in R, you can start getting results.

In this section, we will calculate:

- A mean
- A frequency table
- A simple plot

First, import the data again:

```{r}
data <- read.csv("mydata.csv")
```

## Calculating a Mean

The **mean** is the average.

Let’s calculate the average quiz score:

```{r}
mean(data$quiz_score)
```

The `$` symbol means:

> Use a column from this dataset.

So:

```r
data$quiz_score
```

means:

> The `quiz_score` column inside the dataset called `data`.

## Interpreting the Mean

If R gives you a number such as:

```text
[1] 82.4
```

you can write:

> The average quiz score is 82.4.

::: {.callout-tip}
## Tip

Always explain results in words. Do not only show the code output.
:::

## Calculating Another Mean

You can also calculate the average number of study hours:

```{r}
mean(data$study_hours)
```

A sentence for this result might be:

> Students studied an average of about 6 hours.

## Creating a Frequency Table

A **frequency table** counts how many times each category appears.

Let’s count the number of students in each major:

```{r}
table(data$major)
```

This tells us how many students are listed for each major.

## Interpreting a Frequency Table

If R shows something like:

```text
Biology     Business     Psychology
3           4            3
```

you can write:

> There are 3 Biology students, 4 Business students, and 3 Psychology students in the dataset.

## Another Frequency Table

We can count attendance:

```{r}
table(data$attendance)
```

This shows how many students were marked as `Present` or `Absent`.

## Creating a Simple Plot

A plot helps us see patterns.

Let’s make a scatterplot of study hours and quiz scores:

```{r}
plot(
  data$study_hours,
  data$quiz_score,
  main = "Study Hours and Quiz Score",
  xlab = "Study Hours",
  ylab = "Quiz Score",
  pch = 19,
  col = "steelblue"
)
```

This graph shows whether students who studied more hours tended to have higher quiz scores.

## Another Simple Plot

We can also make a histogram of quiz scores:

```{r}
hist(
  data$quiz_score,
  main = "Distribution of Quiz Scores",
  xlab = "Quiz Score",
  col = "lightblue",
  border = "white"
)
```

A histogram shows how values are spread out.

## Try It Yourself

::: {.callout-note}
## Practice

Use the dataset to answer these questions:

1. What is the average number of study hours?
2. How many students are in each attendance group?
3. Make a plot of sleep hours and quiz score.

Use these commands as a starting point:

```r
mean(data$study_hours)
table(data$attendance)

plot(
  data$sleep_hours,
  data$quiz_score,
  main = "Sleep Hours and Quiz Score",
  xlab = "Sleep Hours",
  ylab = "Quiz Score"
)
```
:::

## Practice: Write Your Results

::: {.callout-note}
## Practice

After running your code, write one sentence for each result.

Example:

> The average quiz score was 81.4.

> Most students in this small dataset were present.

> The scatterplot suggests that higher study hours may be related to higher quiz scores.
:::

## Writing Results in Sentences

Good results include both the number and an explanation.

Instead of only writing:

```text
[1] 6.2
```

write:

> The average number of study hours was 6.2 hours.

Instead of only showing a plot, write:

> The plot suggests that students who studied more hours tended to have higher quiz scores.

::: {.callout-note}
## Reminder

Your goal is not only to run code. Your goal is to understand and explain what the results mean.
:::

## Check Your Understanding

Answer these questions:

1. What does `mean()` calculate?
2. What does `table()` create?
3. What does the `$` symbol do?
4. Why should you explain results in words?

## Summary

In this section, you learned how to:

- Calculate a mean.
- Create a frequency table.
- Make a simple scatterplot.
- Make a histogram.
- Explain results in plain language.