# Common Problems and Solutions

Everyone gets errors in R. Errors are normal.

The important skill is learning how to read the message and try a fix.

## Problem 1: File Not Found

### What You Might See

```text
Error in file(file, "rt") : cannot open the connection
```

or:

```text
No such file or directory
```

### What It Usually Means

R cannot find your file.

### What To Check

Run:

```{r}
getwd()
```



Then check whether `mydata.csv` is inside that folder.

Also run:

```{r}
file.exists("mydata.csv")
```



If the result is `FALSE`, R cannot find the file.

### Possible Fixes

- Move `mydata.csv` into your project folder.
- Check the spelling of the file name.
- Make sure the file ends in `.csv`.
- Make sure you are working in the correct folder.

::: {.callout-warning}
## Common Mistake

`mydata.csv` and `mydata (1).csv` are different file names.
:::

## Problem 2: Package Installation Issues

Sometimes your instructor may ask you to install a package.

Example:

```r
install.packages("ggplot2")
```

### What Can Go Wrong?

- Internet connection problems.
- Typing the package name incorrectly.
- R asks you to restart.
- You do not have permission to install software on the computer.

### Possible Fixes

- Check your internet connection.
- Make sure the package name is inside quotation marks.
- Restart RStudio and try again.
- Ask your instructor or campus IT for help if you are on a lab computer.

::: {.callout-tip}
## Tip

You only need to install a package once on your computer.

But you need to load it with `library()` each time you start a new R session.
:::

## Problem 3: Typing Mistakes

R is very picky about spelling.

These are all different to R:

```r
quiz_score
Quiz_score
quizscore
quiz.score
```

### Common Typing Mistakes

| Mistake | Example | Fix |
|---|---|---|
| Missing quote | `read.csv(mydata.csv)` | `read.csv("mydata.csv")` |
| Misspelled object | `quz_score` | `quiz_score` |
| Missing parenthesis | `mean(data$quiz_score` | `mean(data$quiz_score)` |
| Wrong capitalization | `Read.csv()` | `read.csv()` |

## Problem 4: Working Directory Problems

If R is looking in the wrong folder, it may not find your files.

Check the working directory with:

```{r}
getwd()
```



In RStudio, using an RStudio Project can help keep your working directory organized.

::: {.callout-tip}
## Tip

For each assignment or project, keep your script and data file in the same folder.
:::

## Problem 5: Rendering Errors

When rendering a Quarto document, R runs the code from top to bottom.

A document may fail to render if:

- A file is missing.
- A package is not loaded.
- An object is used before it is created.
- There is a typing mistake in a code chunk.

### Example

This can fail:

```r
mean(data$quiz_score)
```

if `data` was never created earlier in the document.

### Fix

Make sure this line appears first:

```r
data <- read.csv("mydata.csv")
```

## Problem 6: Object Not Found

### What You Might See

```text
Error: object 'data' not found
```

### What It Means

R does not know what `data` is.

### Fix

Create the object first:

```r
data <- read.csv("mydata.csv")
```

Then run your analysis.

## Problem 7: Forgetting Quotation Marks

This is incorrect:

```r
read.csv(mydata.csv)
```

This is correct:

```r
read.csv("mydata.csv")
```

File names must be in quotation marks.

## Troubleshooting Checklist

When something goes wrong, ask:

1. Did I spell everything correctly?
2. Did I use quotation marks around file names?
3. Did I run the earlier lines of code?
4. Is my file in the right folder?
5. Does `file.exists("mydata.csv")` return `TRUE`?
6. Did I close all parentheses?
7. Did I restart RStudio and try again?

::: {.callout-note}
## Encouragement

Errors do not mean you are bad at R.

Errors are part of learning. Read the message, try one fix, and run the code again.
:::

## Practice: Diagnose the Problem

::: {.callout-note}
## Practice

For each example, decide what the problem is.

### Example 1

```r
read.csv(mydata.csv)
```

Question: What is missing?

### Example 2

```r
mean(data$quiz_score
```

Question: What is missing?

### Example 3

```r
Data <- read.csv("mydata.csv")
head(data)
```

Question: Why might this fail?
:::

## Answers

1. Example 1 is missing quotation marks around the file name.
2. Example 2 is missing a closing parenthesis.
3. Example 3 may fail because `Data` and `data` are different names in R.

## Summary

In this section, you learned how to troubleshoot common problems, including:

- File not found errors.
- Package installation issues.
- Typing mistakes.
- Working directory problems.
- Rendering errors.
- Object not found errors.
